TODO

### 2015-06-01 ccs.tex
Fix figure size of update ecosystem
Add section on comparison with other data

\label{sec:android_update_process}
\begin{figure}[h]
 \centering
 \def\svgwidth{0.7\columnwidth}
 \import{figures/}{update_ecosystem.pdf_tex}
 \caption{Flow of updates between participants in the Android ecosystem.
 Numbers on edges indicate updates shipped between \daStartDate\ and \daEndDate, those in brackets represent number of such entities.
 Dotted arrows indicate flows where we can't measure how many updates are produced as they are not public.}
 \label{fig:update_ecosystem}
\end{figure}
To understand how vulnerabilities in Android are fixed we must examine the Android update process which we model in Figure~\ref{fig:update_ecosystem}.
There are five entities or groups which contribute towards Android updates: the network operators, the device manufacturers, the hardware developers, Google and the upstream open source projects.
Android builds on various open source projects such as the Linux kernel, OpenSSL and BouncyCastle cryptography libraries.
Consequently Android can include any compatible versions of those projects, including those which fix security vulnerabilities.
Android also incorporates various drivers for different bits of hardware.
The Android platform is then built from these components by Google.
The code for each Android release or update is kept secret\footnote{\url{https://source.android.com/source/code-lines.html}} until after a binary release has been published.
Device manufacturers likely receive advanced access in order to prepare handsets so they can customise it before passing it on to the network operator.
The network operator may then make or request further customisations and perform further testing before shipping the update to the Device.
Sometimes device manufactures ship updates directly to the user, sometimes the device manufacturer and Google collaborate closely to make a particular phone, such as with Nexus devices.
Sometimes device manufacturers incorporate upstream open source project releases directly, and sometimes incorrectly -- for example previous work has recorded evidence of broken nightly builds of sqlite in Android releases~\cite{Wagner2013}.

@@

>>>>

\label{sec:android_update_process}
\begin{figure}[h]
 \centering
 \def\svgwidth{\columnwidth}
 \import{figures/}{update_ecosystem.pdf_tex}
 \caption{Flow of updates between participants in the Android ecosystem.
 Numbers on edges indicate updates shipped between \daStartDate\ and \daEndDate, those in brackets represent number of such entities.
 Dotted arrows indicate flows where we can't measure how many updates are produced as they are not public.}
 \label{fig:update_ecosystem}
\end{figure}
To understand how vulnerabilities in Android are fixed we must examine the Android update process which we model in Figure~\ref{fig:update_ecosystem}.
There are five entities or groups which contribute towards Android updates: the network operators, the device manufacturers, the hardware developers, Google and the upstream open source projects.
Android builds on various open source projects such as the Linux kernel, OpenSSL and BouncyCastle cryptography libraries.
Consequently Android can include any compatible versions of those projects, including those which fix security vulnerabilities.
Android also incorporates various drivers for different bits of hardware.
The Android platform is then built from these components by Google.
The code for each Android release or update is kept secret\footnote{\url{https://source.android.com/source/code-lines.html}} until after a binary release has been published.
Device manufacturers likely receive advanced access in order to prepare handsets so they can customise it before passing it on to the network operator.
The network operator may then make or request further customisations and perform further testing before shipping the update to the Device.
Sometimes device manufactures ship updates directly to the user, sometimes the device manufacturer and Google collaborate closely to make a particular phone, such as with Nexus devices.
Sometimes device manufacturers incorporate upstream open source project releases directly, and sometimes incorrectly -- for example previous work has recorded evidence of broken nightly builds of sqlite in Android releases~\cite{Wagner2013}.

@@

\section{Comparison with other data}
Here we show that the \da\ data~\cite{Wagner2013} is representative for our purposes by comparing it with two other sources of data which provide an upper and lower bound on it.
The \da\ data is collected from devices across the world where users have voluntarily installed the app.
We have obtained data comparable on 5\,290 devices from a multinational FTSE 100 company's mobile device management database which includes company owned and BYOD devices and from 5\,170\,000 matching User-Agent headers on all HTTP traffic for 30\% of Rwanda for a week.
\begin{figure}
\centering
\includegraphics[width=\columnwidth]{figures/dists}
\caption{Comparison between FTSE, User-Agent and the corresponding \da\ data, error bars indicate 95\% confidence intervals.}
\label{fig:dists}
\end{figure}
We used the data from the FTSE 100 company for the week ending 2015-04-27 and the User-Agent data was collected between 2015-01-31 and 2015-02-12.
Figure~\ref{fig:dists} shows the proportion of devices running each Android OS version in the two comparison data sets and the comparable periods from \da.
The general pattern this shows is that in the FTSE data newer versions are more popular than in the \da\ data and that in the Rwanda data old versions are more popular than in the \da\ data.
This shows that \da\ lies between these two biased samples while being similar to both and so is representative.
